% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Sricharan Chiruvolu} % force lhead all the way left
\rhead{Page \thepage}  % put page number at right
\cfoot{}  % the footer is empty
\pagestyle{fancy} % set pagestyle for the document

\begin{document} 
\thispagestyle{empty} % this page does not have a header
% Center the name over the entire width of resume:
 \name{\large\bf Sricharan Chiruvolu}
\address{ http://sricharan.xyz - mail@sricharan.xyz - (+91) 9035 886166  }


\begin{resume}
\vspace{0.1in}
%\moveleft.5\sectionwidth\centerline{Software/ Computer Science Engineer}  

\section{Education}
\vspace{0.1in} 
		 {\bf B.Tech, Computer Science and Engineering} \hfill 2012-16 \\
			Amrita School of Engineering, Bengaluru, IN. \\
			CGPA (upto 6th semester): 8.71/ 10.00
			
			{\bf Class 12, AP-IPE} \hfill 2010-12 \\
			NRI Junior College, Hyderabad, IN. \\
			Percentage: 91.8\%
			
			{\bf Class 10, CBSE} \hfill 2010 \\
			Kendriya Vidyalaya, Hyderabad, IN. \\
			CGPA: 9.60/ 10.00
			%
		%Passed Class 12 from NRI Junior college, Hyderabad with percentage of
	%
		%Passed Class 10 from Kendriya Vidyalaya, Hyderabad with CGPA of 9.60/ 10.00.
		%
\section{Projects and Internships} 
\vspace{0.1in}
	{\bf Research Intern, RoadRunnr}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[]  -- Ongoing -- 
      \end{itemize}
  {\bf Google Summer of Code}
    \begin{itemize} % Use \item[] to prevent a bullet from appearing
      \item[] Accepted for GSoC program. Assigned to write
				open-source code in association with Google Inc. The goal of
				this project was to improve the lighting system, with support for Point,
				directional, spot and ambient lights. The project was also aimed to implement
				an optimized shadow mapping mechanism(CSM based) with an option to
				toggle it based on the GPU system used.
      \end{itemize}
{\bf Distributed GA for Pharmacogenomic applications} 
       \begin{itemize}
        \item[] A bioinformatics research project on parallel Genetic Algorithms
				implemented on GPGPUs for pharmaco-genomic applications.
    \end{itemize}

  {\bf RayBox} 
        \begin{itemize}
        \item[] An image synthesis system based on ray-tracing which includes
					reflections, refractions, soft shadows and depth of field.
       \end{itemize}

   {\bf  ClassBox} 
        \begin{itemize}
        \item[]  A complete productivity suite for schools and colleges to interact
								effectively. Features include an interactive drawing board, chat rooms,
								dedicated forums, quiz generation and analytics, push notifications e.t.c.
       \end{itemize} 
		
		{\bf  Other hobby projects} 
        \begin{itemize}
        \item[]  A few hobby projects on various aspects of computer
								science and engineering are hosted at \bf{ http://github.com/sricharanized}.
       \end{itemize} 

\section{Technical Skills} 
\vspace{0.1in} 
    {\bf Operating System}: Various Flavours of GNU/Linux\\
    {\bf Programming Languages}: Python, C++, Javascript, C and Java \\
		{\bf Dev Tools}: emacs, vim, gdb, git, mercurial, bash \\
		{\bf Frameworks and Libraries}: OpenGL/ GLSL, Django, AngularJS, MeteorJS
 
%\section{EMPLOYMENT} 
%\vspace{0.1in} 
    %{\bf Lecturer,} Department of Language, Literature and 
    %Communication, Rensselaer Polytechnic Institute, Troy, NY 
    %1986-1987 
 %
    %{\bf Teaching Assistant,} Department of Language, Literature and 
    %Communication, Rensselaer Polytechnic Institute  1985-1986 
 %
    %{\bf Instructor and Lecturer,} Department of English and 
    %Communications, North Adams State College, North Adams, MA 
    %1985 - 1986 
 %
    %{\bf Workshop Leader,} North Adams State College, North Adams, MA \\
    %"Composition for Teachers: A Writing Across the Disciplines 
    %Approach." Graduate School of Education, 1986; \\
    %``Effective Writing for Executives.'' Professional Development 
    %Program, 1985; ``Informative and Persuasive Business Writing.''
    %Winter Study, 1983 
 %
    %{\bf Writing Consultant,} Graduate School of Education, North Adams 
    %State College, North Adams, MA  1985 
 %
    %{\bf Research Assistant,} Chesterwood, Stockbridge, MA  Summer 1985 
 %
    %{\bf Instructor,} Learning Skills Center, North Adams State 
    %College, North Adams, MA  1979 - 1985 
 %
    %{\bf Acting Program Coordinator for Academic Tutoring and 
    %Advising,} Learning Skills Center, North Adams State College, 
    %North Adams, MA  Spring 1985 
 %
    %{\bf English Teacher,} Easthampton High School, Easthampton, MA and 
    %West Orange, NJ.  Chair, English Department evaluation; 
    %member, Alternative Learning Program.  1968 - 1979 
 %
 
\section{Achievements} 
\vspace{0.1in} 
	
    Honorable mention (team) - ACM-ICPC Asia Amritapuri regionals 2015 \\
		Honorable mention (team) - ACM-ICPC Asia Chennai regionals 2015 \\
		Executive member/ Office Bearer - Forum for Aspiring Computer Engineers, 2014-15 \\
    Finalist (team) - InCTF (India's largest capture the flag style ethical hacking challenge), 2015 \\
		Event Head - Appalanche (An 8 hour Hackathon), Ekatva - 2015 \\
		Executive member/ Office Bearer - GNU/ UNIX User Group, Bangalore Chapter - 2015
	
\section{Magazine Publications} 
\vspace{0.1in}
``Open-Source Licensing Guide,'' {\it Open Source for You, Nov. 2015} \\
``Getting Started with Dart,'' {\it Open Source for You, Oct. 2015} \\
``How students can contribute to FOSS,'' {\it Open Source for You, Aug. 2015} \\
``Generating Graphics with OpenGL,'' {\it Open Source for You, July. 2015} 


\section{Other Information} 
\vspace{0.1in} 
    {\bf Github}: http://github.com/sricharanized \\
    {\bf Date of Birth}: 12th October 1994 \\
		{\bf Linguistic Proficiency}: English, Hindi and Telugu \\
		{\bf Hobbies}: Reading Manga, Watching Anime and Sitcoms 

\end{resume}
\end{document}






























