\documentclass[margin]{res}  
\textwidth=5.2in 
\begin{document} 

\address{\Large {\bf{Sricharan Chiruvolu}}\\[10pt]{\sl (+91) 9035 886166 } \\ {\sl \underline{sricharanized@gmail.com}}
        }
\address{Mathura block \\ Amrita School of Engineering  \\
         Kasavanahalli, Carmelaram P.O.\\ Bengaluru, India - 560035}
 
\begin{resume}

%\section{Summary} 
	%To associate with a vibrant organization, to fully utilize my knowledge, skills and contribute to overall growth of the organization.
	
%\section{Interests} 
 %Website design and development, computer graphics, free and open source software

\section{Academic Qualifications}
{\bf B.Tech, 7th Semester} {\sl \hfill 2012-2016}
 \\Computer Science and Engineering\\ Amrita School of Engineering, Bengaluru {\sl \hfill CGPA(current) {\bf 8.71/ 10.00}}

{\bf 12th Grade} {\sl \hfill 2012}
\\NRI Junior College, Hyderabad{\sl \hfill Percentage {\bf 91.6\% }}

{\bf 10th Grade}{\sl \hfill 2010}
 \\ Kendriya Vidyalaya, Hyderabad{\sl \hfill CGPA {\bf 9.60/ 10.00}}


\section{Experience}
	
	{\bf Student Developer, Google Summer of Code} \hfill {\sl Summer 2015}
	\\{\sl Google Inc.}
	\begin{itemize}
	\item Developing open source software with Google Inc. sponsorship for PySoy (Copyleft Games), a 3D cloud game engine written in Python.
 \item Development includes enhancement in the lighting and shadow rendering, reproducing and fixing bugs, documentation and testing. Programming languages include Genie, GLSL, Python and C. 
	\item More information on my project can be found at: {\sl \underline{http://goo.gl/frUCNa}} and {\sl \underline{http://copyleftgames.org}}.
	\end{itemize}
% {\bf Introductory course on Linux}- LFS101x.2 {\sl \hfill Winter 2014}
%	\\{\sl LinuxFoundationX}
%	\\Successfully completed a certification course with an Honor Code certificate, offered by the Linux Foundation online.
	
	{\bf J2SE professional certification} {\sl \hfill Summer 2014 }
	\\{\sl Aptech India Private Ltd.}
	\\Successfully completed a certification course on Java programming and application development.

 {\bf In-plant training} {\sl \hfill Winter 2013} 
 \\{\sl HCL Technologies}
 \\Gained industrial exposure of software development. Attended workshops on Android application development, PC hardware e.t.c.

\section{Technical Expertise}

\begin{tabular}{l p{3.5in}}
    \underline{Intermediate Proficiency:} & Web design and development - Python(Django and Flask) and Javascript stack, 3D programming - OpenGL and GLSL, Free and open-source software, IDE's: qtCreator, codeblocks, matlab - Image Processing Toolkit, android studio, eclipse\\
		
		\underline{Knowledgeable:} & Build tools - Cmake and GNU make, version control systems - git and mercurial, designing - Adobe Photoshop and Illustrator, documentation: Doxygen (generation) and LaTeX (preparation)
  \end{tabular}
	\\\\
\section{Open-source Contributions}
{\bf Copyleftgames} \begin{itemize} \item Worked on reproducing and fixing bugs, enhancing the physics engine and game render cycles. \item A student developer for Pysoy under Google Summer of Code program. Working on enhancement in the lighting and shadow rendering.
%\item {\sl Details: \underline{http://copyleftgames.org/} and \underline{http://goo.gl/frUCNa}}
 \end{itemize}

{\bf Codrspace} \begin{itemize} \item Worked on minor enhancements of the python backend.\item Currently working as a UI/UX developer.  \item {\sl Details: \underline{http://codrspace.com/}} \end{itemize}


 \section{Projects done}
{\bf RayBox} \hfill Jan 2015 \\ RayBox is an image synthesis system based on ray-tracing which includes reflections, refractions, soft shadows and depth of field.

{\bf ClubBox} \hfill Nov 2014 \\ Developed a python based club management system where club in 
charges and faculty can interact with the club executives and organized events effectively.

{\bf ScreamBox} \hfill May 2014 \\ Developed a blogging website using Django Framework where users can blog, follow others send personal messages and interact.\\ Currently hosted at \underline{http://sricharan.herokuapp.com/}.

{\bf Personal Projects} \\ Developed various OpenGL based models, a maze-solver using image processing techniques, a simple loadable kernel module, a google app engine based blogging site, a few bash scripts, scripts using Twitter, Facebook graph, openweather and various other RESTful APIs e.t.c. \\Details: \underline{http://github.com/sricharanized/}.

 \section{Ongoing Projects}
{\bf ClassBox} \\ A complete productivity suite for schools and colleges to interact effectively. Features include an interactive drawing board, chat rooms, dedicated forums, quiz generation and analytics, push notifications e.t.c. This application is being developed using MEAN javascript stack. A companion android application is also under development.


\section{Volunteer  Activities} 
{\bf Executive member/Office bearer}\hfill  2014-2015\\ Forum for Aspiring Computer Engineers [FACE] \\ Conducted seminars and workshops that are aimed at imparting knowledge in the field of computer science at Amrita School of Engineering, Bengaluru. \\ Details: \underline{https://faceaseb.wordpress.com}

\section{Publications}
{\bf Generating Graphics with OpenGL}\hfill July 2015\\
{\sl Open Source For You} - Asia's first Publication on Free and Open Source Software}
{\bf Source Code Management using Git}\hfill May 2015\\
{\sl Technical Article for Sanchita'15} - Annual Magazine for Amrita School of Engineering, Bangalore}

                
%\section{Hobbies}
%Enjoying sitcoms, reading manga (Japanese comics), watching anime.

\section{Personal Details}
\begin{tabular}{l p{3.5in}}
      \bf{Date of Birth} & \hfill 12th October 1994\\
			\bf{Linguistic Proficiency} & \hfill  English, Hindi and Telugu\\
 \end{tabular}
\section{Links}
\begin{tabular}{l p{3.5in}}
      \bf{Website} & \hfill \underline{http://sricharanized.github.io/}\\
			\bf{Github} & \hfill  \underline{http://github.com/sricharanized/}\\
			\bf{LinkedIn} & \hfill  \underline{http://in.linkedin.com/in/sricharanchiruvolu/}\\
 \end{tabular}


\end{resume}
\end{document} 

